Designing Types for R, Empirically

### 2020-09-13 paper/main.tex
numbers and tables updated, smoothing wording now and fleshing out extra discussions

\renewcommand{\null}{\texttt{\textbf{null}}\xspace}
\newcommand{\scalar}{\texttt{\textbf{scalar}}\xspace}
\renewcommand{\vector}{\texttt{\textbf{vector}}\xspace}
\newcommand{\class}{\texttt{\textbf{class}}\xspace}
\newcommand{\any}{\texttt{\textbf{any}}\xspace}
\newcommand{\environment}{\texttt{\textbf{env}}\xspace}
\newcommand{\expression}{\texttt{\textbf{expression}}\xspace}
\newcommand{\Language}{\texttt{\textbf{lang}}\xspace} %% Upper case!
\newcommand{\externalptr}{\texttt{\textbf{externalptr}}\xspace}
\renewcommand{\symbol}{\texttt{\textbf{symbol}}\xspace}
\newcommand{\pairlist}{\texttt{\textbf{pairlist}}\xspace}
\newcommand{\weakref}{\texttt{\textbf{weakref}}\xspace}
\renewcommand{\int}{\texttt{\textbf{int}}\xspace}
\newcommand{\chr}{\texttt{\textbf{chr}}\xspace}
\newcommand{\dbl}{\texttt{\textbf{dbl}}\xspace}
\newcommand{\lgl}{\texttt{\textbf{lgl}}\xspace}
\newcommand{\clx}{\texttt{\textbf{clx}}\xspace}
\newcommand{\raw}{\texttt{\textbf{raw}}\xspace}
\newcommand{\NA}{\texttt{{NA}}\xspace}
\newcommand{\VARGS}{\texttt{\textbf{...}}\xspace}
\newcommand{\T}{\ensuremath{T}\xspace}
\renewcommand{\S}{\ensuremath{S}\xspace}
\newcommand{\V}{\ensuremath{V}\xspace}
\newcommand{\A}{\ensuremath{A}\xspace}
\newcommand{\ID}{\ensuremath{ID}\xspace}
\newcommand{\F}{\ensuremath{F}\xspace}
\newcommand{\B}{\ensuremath{B}\xspace}
\newcommand{\FUN}[2]{\ensuremath{\langle #1 \rangle \rightarrow #2}\xspace}
\newcommand{\STRUCT}[1]{\texttt{\textbf{struct}}\ensuremath{\langle #1\rangle}\xspace}
\newcommand{\LIST}[1]{\texttt{\textbf{list}}\ensuremath{\langle #1\rangle}\xspace}
\newcommand{\CLASS}[1]{\texttt{\textbf{class}}\ensuremath{\langle #1\rangle}\xspace}
\newcommand{\VEC}[1]{#1\k{[]}\xspace}
\newcommand{\NAVEC}[1]{\k{\string^}\!#1\k{[]}\xspace}

@@

\begin{document}
\title{Designing Types for R, Empirically}
\author{Alexi Turcotte}\affiliation{\institution{Northeastern University}}
\author{Aviral Goel}\affiliation{\institution{Northeastern University}}
\author{Filip Krikava}\affiliation{\institution{Czech Technical University in Prague}}
\author{Jan Vitek}\affiliation{\institution{Norteastern / Czech Technical University}}

\newcommand{\NUMFUNCTIONS}{20,214\xspace}  %%% TODO auto-gen
\newcommand{\NUMPACKAGES}{412\xspace}  %%% TODO auto-gen
\newcommand{\PACKAGES}{412\xspace}  %%% TODO auto-gen
\newcommand{\genthat}{genthat\xspace}  %%% TODO auto-gen
\newcommand{\YEARS}{20\xspace} %%TODO fix
\newcommand{\PERCFAILEDASSERTIONS}{2.19\%\xspace}
\newcommand{\PERCFAILEDASSERTIONSWUNDEF}{2.23\%\xspace}
\newcommand{\PERCASSERTIONSUNDEF}{0.04\%\xspace}
\newcommand{\NUMPKGSEVAL}{7485\xspace} % autogenerate
\newcommand{\NUMASSERTIONS}{62,171,573\xspace} %autogenerate
\newcommand{\PROPFUNSFAILEDCHECK}{21.21\%\xspace}
\newcommand{\PROPFUNSFAILEDCHECKNOSTHREE}{15.48\%\xspace} 
\newcommand{\PROPARGSFAILINGASSERTS}{3.53\%\xspace} % autogen....
\newcommand{\PERCSUCCARG}{96.46\%\xspace}
\newcommand{\PERCSUCCFUNNOSTHREE}{84.52\%\xspace}
\newcommand{\PERCSUCCFUNS}{78.79\%\xspace}
\newcommand{\PERCCALLSBADFUNSINTESTS}{5.38\%\xspace}
\newcommand{\TOTNUMSIGS}{21,730\xspace}
\newcommand{\PROPSTRUCTSDYN}{44.46\%\xspace}
\newcommand{\NUMFILESRUN}{145,373\xspace}

@@

R has one builtin notion of type that can be queried by the \k{typeof}
function. Figure~\ref{rtypes} lists all of the builtin types that are
provided by the language, which are the possible return values of
\k{typeof}. There is no intrinsic notion of subtyping in R, but in many
context a \k{logical} will convert to \k{integer}, and an \k{integer} will
convert to \k{double}.  Some odd conversions can occur in corner cases, such
as \k{1<"2"} holds and \k{c(1,2)[1.6]} returns the first element of the
vector, as the double is converted to an integer. R does not distinguish
between scalars and vectors (they are all vectors), so \code{typeof(5) ==}
\code{typeof(c(5)) == typeof(c(5,5))} \code{ == "double"}. Finally all
vectorized data types have a distinguished missing value denoted by
\code{NA}. The default type of \code{NA} is \k{logical}. We can see that
\code{typeof(NA)=="logical"}, but NA inhabits every type:
\code{typeof(c(1,NA)[2])=="double"}.

@@

\begin{table}[!h]
% BEGIN Autogenerated
\small\begin{tabular}{lrrrr}\toprule
Type & Args & \% of Args & Observations & \% of Obs.\\\midrule
\dbl               & 13,255 &     11.0 &  41,560,797 & 1.5\\
\lgl               & 10,142 &      8.4 & 712,895,959 & 27.2\\
\null              &  9,175 &      7.6 & 122,202,183 & 4.6\\
\chr               &  9,171 &      7.5 & 794,058,588 & 30.3\\
\VEC\dbl           &  7,811 &      6.5 &  29,272,232 & 1.1\\
\VARGS             &  7,759 &      6.4 &  76,369,333 & 2.9\\
\any               &  6,243 &      5.2 & 255,539,497 & 9.0\\
\VEC\chr           &  4,576 &      3.8 &  88,233,523 & 3.3\\
\CLASS{\texttt{matrix}}     & 4,522 & 3.7 & 32,452,555 & 1.2\\
\CLASS{\texttt{data.fram}e} & 2,781 & 2.3 &  7,749,094 & 0.3\\
\bottomrule
\end{tabular}
\caption{Top types of arguments in R}\label{ctb}
\end{table}

@@

\begin{table}
% BEGIN Autogenerated
\small
\begin{tabular}{llrrr}
\toprule
Passed & Arg Type & Occurrences & \% Total & Cumulative \%\\
\midrule
\VEC\dbl & \CLASS{\texttt{matrix}} & 371,896 & 27.37 & 27.37\\
\VEC\dbl & \VEC\int & 117,212 & 8.62 & 35.99\\
\chr & \CLASS{\texttt{bignum}} | \VEC\raw & 100,100 & 7.37 & 43.36\\
\dbl & \int | \null & 60,578 & 4.46 & 47.81\\
\VEC\dbl & \CLASS{\texttt{timeSeries}} & 58,872 & 4.33 & 52.15\\
\addlinespace
\CLASS{\texttt{matrix}} & \CLASS{\texttt{timeSeries}} & 55,005 & 4.05 & 56.19\\
\VEC\dbl & \dbl & 53,338 & 3.92 & 60.12\\
\dbl & \CLASS{\texttt{data.frame}} & 32,553 & 2.40 & 62.51\\
\VEC\dbl & \CLASS{\texttt{data.frame}} & 31,576 & 2.32 & 64.84\\
\dbl & \int & 20,586 & 1.51 & 66.35\\
\bottomrule
\end{tabular}
% END Autogenerated
\caption{Top contract failures}
\label{tbl:fail-breakdown-0}
\end{table}

@@

 \begin{table}
% BEGIN Autogenerated
\small
\begin{tabular}{llrrr}
\toprule
Passed & Arg Type & \# Args Failed & \# Args with Type & \% Failure\\
\midrule
\VEC\dbl & \CLASS{\texttt{matrix}} & 15 & 1394 & 1.08\\
\VEC\dbl & \VEC\int & 44 & 657 & 6.70\\
\chr & \CLASS{\texttt{bignum}} | \VEC\raw & 1 & 3 & 33.33\\
\dbl & \int | \null & 5 & 20 & 25.00\\
\VEC\dbl & \CLASS{\texttt{timeSeries}} &19 & 35 & 54.29\\
\addlinespace
\CLASS{\texttt{matrix}} & \CLASS{\texttt{timeSeries}} &  19 & 35 & 54.29\\
\VEC\dbl & \dbl & 100 & 5021 & 1.99\\
\dbl & \CLASS{\texttt{data.frame}} &  1 & 900 & 0.11\\
\VEC\dbl & \CLASS{\texttt{data.frame}} &  6 & 900 & 0.67\\
\dbl & \int & 48 & 529 & 9.07\\
\bottomrule
\end{tabular}

@@

 \begin{table}
% BEGIN Autogenerated\
\small
\begin{tabular}{llrrr}
\toprule
Passed & Arg Type & \# Args Failed & \# Args with Type & \% Failure\\
\midrule
\VEC\dbl & \VEC\int & 44 & 657 & 6.70\\
\NAVEC\lgl & \null & 158 & 2756 & 5.73\\
\VEC\chr & \chr & 183 & 4102 & 4.46\\
\chr & \null & 117 & 2756 & 4.25\\
\dbl & \null & 107 & 2756 & 3.88\\
\bottomrule
\end{tabular}
% END Autogenerated
 \caption{What is the highest failure rate among popular argument types? For argument signatures whose frequency is in the 90th percentile}
 \label{tbl:fail-breakdown-2}
 \end{table}

  \begin{table}
% BEGIN Autogenerated
\small
\begin{tabular}{ll@{}rrr@{}}
\toprule
Passed & Arg Type & \#Args Fail & \#Args w Type & \% Failure\\
\midrule
\CLASS{\texttt{data.frame}} & \CLASS{\texttt{data.frame}, \texttt{tbl}, \texttt{tbl\_df}} & 63 & 284 & 22.18\\
\CLASS{\texttt{matrix}} & \CLASS{\texttt{array}} & 13 & 70 & 18.57\\
\NAVEC\lgl & \lgl | \null & 9 & 49 & 18.37\\
\VEC\chr & \LIST{\VEC\chr} & 20 & 109 & 18.35\\
\VEC\clx & \clx & 7 & 42 & 16.67\\
\bottomrule
\end{tabular}
% END Autogenerated
 \caption{What is the highest failure rate among popular argument types? For argument signatures whose frequency is in the 80th percentile}
 \label{tbl:fail-breakdown-3}
 \end{table}

>>>>

\renewcommand{\null}{\texttt{\textbf{null}}\xspace}
\newcommand{\scalar}{\texttt{\textbf{scalar}}\xspace}
\renewcommand{\vector}{\texttt{\textbf{vector}}\xspace}
\newcommand{\class}{\texttt{\textbf{class}}\xspace}
\newcommand{\any}{\texttt{\textbf{any}}\xspace}
\newcommand{\environment}{\texttt{\textbf{env}}\xspace}
\newcommand{\expression}{\texttt{\textbf{expression}}\xspace}
\newcommand{\Language}{\texttt{\textbf{lang}}\xspace} %% Upper case!
\newcommand{\externalptr}{\texttt{\textbf{externalptr}}\xspace}
\renewcommand{\symbol}{\texttt{\textbf{symbol}}\xspace}
\newcommand{\pairlist}{\texttt{\textbf{pairlist}}\xspace}
\newcommand{\weakref}{\texttt{\textbf{weakref}}\xspace}
\renewcommand{\int}{\texttt{\textbf{int}}\xspace}
\newcommand{\chr}{\texttt{\textbf{chr}}\xspace}
\newcommand{\dbl}{\texttt{\textbf{dbl}}\xspace}
\newcommand{\lgl}{\texttt{\textbf{lgl}}\xspace}
\newcommand{\clx}{\texttt{\textbf{clx}}\xspace}
\newcommand{\raw}{\texttt{\textbf{raw}}\xspace}
\newcommand{\NA}{\texttt{{NA}}\xspace}
\newcommand{\VARGS}{\texttt{\textbf{...}}\xspace}
\newcommand{\T}{\ensuremath{T}\xspace}
\renewcommand{\S}{\ensuremath{S}\xspace}
\newcommand{\V}{\ensuremath{V}\xspace}
\newcommand{\A}{\ensuremath{A}\xspace}
\newcommand{\ID}{\ensuremath{ID}\xspace}
\newcommand{\F}{\ensuremath{F}\xspace}
\newcommand{\B}{\ensuremath{B}\xspace}
\newcommand{\FUN}[2]{\ensuremath{\langle #1 \rangle \rightarrow #2}\xspace}
\newcommand{\STRUCT}[1]{\texttt{\textbf{struct}}\ensuremath{\langle #1\rangle}\xspace}
\newcommand{\LIST}[1]{\texttt{\textbf{list}}\ensuremath{\langle #1\rangle}\xspace}
\newcommand{\CLASS}[1]{\texttt{\textbf{class}}\ensuremath{\langle #1\rangle}\xspace}
\newcommand{\VEC}[1]{#1\k{[]}\xspace}
\newcommand{\NAVEC}[1]{\k{\string^}\!#1\k{[]}\xspace}
\newcommand{\NASCA}[1]{\k{\string^}\!#1\xspace}

@@

\begin{document}
\title{Designing Types for R, Empirically}
\author{Alexi Turcotte}\affiliation{\institution{Northeastern University}}
\author{Aviral Goel}\affiliation{\institution{Northeastern University}}
\author{Filip Krikava}\affiliation{\institution{Czech Technical University in Prague}}
\author{Jan Vitek}\affiliation{\institution{Nortjeastern / Czech Technical University}}

\newcommand{\NUMFUNCTIONS}{25,215\xspace}  %%% TODO auto-gen
\newcommand{\NUMPACKAGES}{412\xspace}  %%% TODO auto-gen
\newcommand{\PACKAGES}{412\xspace}  %%% TODO auto-gen
\newcommand{\genthat}{genthat\xspace}  %%% TODO auto-gen
\newcommand{\YEARS}{20\xspace} %%TODO fix
\newcommand{\PERCFAILEDASSERTIONS}{2.05\%\xspace}
\newcommand{\PERCFAILEDASSERTIONSWUNDEF}{1.98\%\xspace}
\newcommand{\PERCASSERTIONSUNDEF}{0.07\%\xspace}
\newcommand{\NUMPKGSEVAL}{8,694\xspace} % autogenerate
\newcommand{\NUMASSERTIONS}{98,105,161\xspace} %autogenerate
\newcommand{\PROPFUNSFAILEDCHECK}{12.29\%\xspace}
\newcommand{\PROPFUNSFAILEDCHECKNOSTHREE}{10.30\%\xspace} 
\newcommand{\PROPARGSFAILINGASSERTS}{2.40\%\xspace} % autogen....
\newcommand{\PERCSUCCARG}{97.60\%\xspace}
\newcommand{\PERCSUCCFUNNOSTHREE}{89.70\%\xspace}
\newcommand{\PERCSUCCFUNS}{87.70\%\xspace}
\newcommand{\PERCCALLSBADFUNSINTESTS}{2.73\%\xspace}
\newcommand{\TOTNUMSIGS}{21,730\xspace}
\newcommand{\PROPSTRUCTSDYN}{65.97\%\xspace}
\newcommand{\NUMFILESRUN}{160,379\xspace}
\newcommand{\NUMFILESREVDEPS}{153,806\xspace}
\newcommand{\NUMFILESKAGGLE}{6,573\xspace}

@@

R has one builtin notion of type that can be queried by the \k{typeof}
function. Figure~\ref{rtypes} lists all of the builtin types that are
provided by the language, which are the possible return values of
\k{typeof}. There is no intrinsic notion of subtyping in R, but in many
context a \k{logical} will convert to \k{integer}, and an \k{integer} will
convert to \k{double}.  Some odd conversions can occur in corner cases, such
as \k{1<"2"} holds and \k{c(1,2)[1.6]} returns the first element of the
vector, as the double is converted to an integer. R does not distinguish
between scalars and vectors (they are all vectors), so \code{typeof(5) ==}
\code{typeof(c(5)) == typeof(c(5,5))} \code{ == "double"}.

All vectorized data types have a distinguished missing value denoted by \code{NA}. 
The default type of \code{NA} is \k{logical}. 
We can see that \code{typeof(NA)=="logical"}, but NA inhabits every type: \code{typeof(c(1,NA)[2])=="double"}.
In addition to \code{NA}, R has a \code{NULL} value, and to understand why R has both a \code{NULL} value and \code{NA} values it is useful to remember that R is primarily designed for statistics and data science.
In experimental data science, it is useful to have a notion of a ``missing observation'', which is often NaN (not a number, or similar) in, e.g., MATLAB and Python.
Since vectors are unityped in R, it {\it must} have a ``NaN'' value for each primitive type, hence the \code{NA}s, while there is only a single \code{NULL} null-typed value in the language to encompass all other cases.

@@

\begin{table}[!h]
% BEGIN Autogenerated
\small\begin{tabular}{lrrrr}\toprule
Type & Args & \% of Args & Observations & \% of Obs.\\\midrule
\dbl               & 12,298 &     11.24 &  12,152,787 & 20.3 \\
\lgl               & 9,366 &      8.7 & 6,650,294 & 11.1 \\
\null              &  8,799 &      8.0 & 2,187,611 & 3.7 \\
\chr               &  8,727 &      8.0 & 2,564,207 & 4.3 \\
\VEC\dbl           &  7,190 &      6.6 &  4,934,773 & 8.2 \\
\VARGS             &  6,611 &      6.0 &  6,075,874 & 10.1 \\
\any               &  6,120 &      5.6 & 339,299 & 0.6 \\
\VEC\chr           &  4,325 &      4.0 &  1,060,466 & 1.8 \\
\CLASS{\texttt{matrix}}     & 4,152 & 3.8 & 2,805,718 & 4.7 \\
\CLASS{\texttt{data.frame}} & 2,608 & 2.4 &  352,655 & 0.6 \\
\bottomrule
\end{tabular}
\caption{Top types of arguments in R}\label{ctb}
\end{table}

@@

\begin{table}
% BEGIN Autogenerated
\small
\begin{tabular}{llrrr}
\toprule
Passed & Arg Type & Occurrences & \% Total & Cumulative \%\\
\midrule
\VEC\dbl & \CLASS{\texttt{matrix}} & 705,036 & 36.36 & 36.36 \\ 
\VEC\dbl & \VEC\int & 189,800 & 9.79 & 46.15 \\ 
\chr & \CLASS{\texttt{bignum}} | \VEC\raw & 100,100 & 5.16 & 51.31 \\
\CLASS{{\tt simpleError, error, condition}} & \CLASS{{\tt data.frame}} | \CLASS{{\tt matrix}} | \CLASS{{\tt randomForest}} | \VEC\dbl & 78,197 & 4.03 & 55.34 \\ 
  \CLASS{{\tt data.frame}} & \CLASS{{\tt data.frame, tbl, tbl\_df}} & 58,809 & 3.03 & 58.37 \\ 
  \CLASS{{\tt matrix}} & \CLASS{{\tt timeSeries}} & 53,482 & 2.76 & 61.13 \\ 
 \VEC\dbl & \VEC\int & 33,350 & 1.72 & 62.85 \\ 
 \dbl & \CLASS{{\tt data.frame}} & 32261 & 1.66 & 64.52 \\ 
  \VEC\dbl & \CLASS{{\tt data.frame}} & 31361 & 1.62 & 66.13 \\ 
  \CLASS{{\tt xml\_node}} & \CLASS{{\tt xml\_missing}} $|$ \CLASS{{\tt xml\_nodeset}} $|$ \CLASS{{\tt xml\_document, xml\_node}} & 30,330 & 1.56 & 67.70 \\ 
\bottomrule
\end{tabular}
% END Autogenerated
\caption{Top contract failures}
\label{tbl:fail-breakdown-0}
\end{table}

@@

 \begin{table}
% BEGIN Autogenerated
\small
\begin{tabular}{llrrr}
\toprule
Passed & Arg Type & \# Args Failed & \# Args with Type & \% Failure\\
\VEC\dbl & \CLASS{\texttt{matrix}} & 18 & 1522 & 1.18 \\ 
\VEC\dbl & \VEC\int  & 66 & 5865 & 1.13 \\ 
\chr & \CLASS{\texttt{bignum}} | \VEC\raw & 1 & 3 & 33.33 \\ 
\CLASS{{\tt simpleError, error, condition}} & \CLASS{{\tt data.frame}} | \CLASS{{\tt matrix}} | \CLASS{{\tt randomForest}} | \VEC\dbl & 2 & 2 & 100 \\ 
  \CLASS{{\tt data.frame}} & \CLASS{{\tt data.frame, tbl, tbl\_df}} & 23 & 196 & 11.73 \\ 
  \CLASS{{\tt matrix}} & \CLASS{{\tt timeSeries}} & 21 & 39 & 53.85 \\ 
 \VEC\dbl & \VEC\int & 31 & 624 & 4.97 \\ 
 \dbl & \CLASS{{\tt data.frame}} & 2 & 1025 & 0.20 \\ 
  \VEC\dbl & \CLASS{{\tt data.frame}}  & 6 & 1025 & 0.59 \\ 
  \CLASS{{\tt xml\_node}} & \CLASS{{\tt xml\_missing}} $|$ \CLASS{{\tt xml\_nodeset}} $|$ \CLASS{{\tt xml\_document, xml\_node}}  & 1 & 1 & 100 \\ 
\bottomrule
\end{tabular}

@@

 \begin{table}
% BEGIN Autogenerated\
\small
\begin{tabular}{llrrr}
\toprule
Passed & Arg Type & \# Args Failed & \# Args with Type & \% Failure\\
\midrule
\VEC\dbl & \VEC\int & 31 & 624 & 4.97 \\
\dbl & \int & 21 & 519 & 4.05\\
\VEC\chr & \chr | \null & 10 & 256 & 3.91 \\
\NAVEC\lgl & \VEC\lgl & 8  & 219 & 3.65 \\
\NASCA\lgl & \VEC\lgl & 5 & 219 & 2.28 \\
\bottomrule
\end{tabular}
% END Autogenerated
 \caption{What is the highest failure rate among popular argument types? For argument signatures whose frequency is in the 90th percentile}
 \label{tbl:fail-breakdown-2}
 \end{table}

  \begin{table}
% BEGIN Autogenerated
\small
\begin{tabular}{ll@{}rrr@{}}
\toprule
Passed & Arg Type & \#Args Fail & \#Args w Type & \% Failure\\
\midrule
\CLASS{{\tt matrix}} & \CLASS{{\tt timeSeries}} & 21 & 39 & 35.90 \\
\VEC\dbl & \CLASS{{\tt timeSeries}} & 21 & 39 & 35.90 \\
\CLASS{{\tt data.frame}} & \CLASS{{\tt timeSeries}} & 14 & 39 & 35.90 \\
\CLASS{{\tt dtplyr\_step\_first, dtplyr\_step}} & \CLASS{{\tt data.frame}} | Grouped Tibble | Tibble & 10 & 45 & 22.22 \\
\chr & \raw & 6 & 31 & 19.35 \\
% \CLASS{\texttt{data.frame}} & \CLASS{\texttt{data.frame}, \texttt{tbl}, \texttt{tbl\_df}} & 63 & 284 & 22.18\\
% \CLASS{\texttt{matrix}} & \CLASS{\texttt{array}} & 13 & 70 & 18.57\\
% \NAVEC\lgl & \lgl | \null & 9 & 49 & 18.37\\
% \VEC\chr & \LIST{\VEC\chr} & 20 & 109 & 18.35\\
% \VEC\clx & \clx & 7 & 42 & 16.67\\
\bottomrule
\end{tabular}
% END Autogenerated
 \caption{What is the highest failure rate among popular argument types? For argument signatures whose frequency is in the 80th percentile.
 *: Grouped Tibble is \CLASS{{\tt data.frame, grouped\_df, tbl, tbl\_df}} , and Tibble is \CLASS{{\tt data.frame, grouped\_df, tbl, tbl\_df}}.
 \AT{TODO Fix this table.}}
 \label{tbl:fail-breakdown-3}
 \end{table}
